Daily goals

### 2020-07-01 2-body.Rmd
adding todos

Automated sequence gathering pipelines have been an important incorporation to the field of phylogenetics in many ways, particularly because they represent a clear step towards reproducibility in the field. In contrast, most published phylogenies to date have been inferred using alignments that have been assembled and curated "by hand" [@morrison2009would].
Automated approaches often suffer from errors in homology inference that could rapidly caught by human oversight. CITATION
Many systemacists support a classic phylogenetics approach (few markers thoughtfully curated) over the genomics approach (a massive amount of DNA markers that will overcome potential errors in the alignment coming from a lack of human curation).
Species tree reconstructions from multi-gene data sets taking into account the multispecies coalescent model are considered the gold standard for inferring species relationships [@song2012resolving; ROJAS ET AL.].
It has also been suggested that manual curation of locus alignments produces better phylogenetic reconstructions and this has been demonstrated for genomic alignments [@fragoso2017pilot].

>>>>

Automated sequence gathering pipelines have been an important incorporation to the field of phylogenetics in many ways, particularly because they represent a clear step towards reproducibility in the field. In contrast, most published phylogenies to date have been inferred using alignments that have been assembled and curated "by hand" [@morrison2009would].
Automated approaches often suffer from errors in homology inference that could rapidly caught by human oversight. CITATION
Many systemacists support a classic phylogenetics approach (few markers thoughtfully curated) over the genomics approach (a massive amount of DNA markers that will overcome potential errors in the alignment coming from a lack of human curation).
Species tree reconstructions from multi-gene data sets taking into account the multispecies coalescent model are considered the gold standard for inferring species relationships [@song2012resolving; ROJAS ET AL. bats paper, take citations from there].
It has also been suggested that manual curation of locus alignments produces better phylogenetic reconstructions and this has been demonstrated for genomic alignments [@fragoso2017pilot].

### 2020-07-01 _TODO.Rmd
adding todos

>>>>

- [ ] hammer home the message that gene alignments are the gold standard for phylogenetics in many ways:
  - [ ] genomic data, uces, radseqs are not comparable to other data
  - [ ] homology in genomic data is not fully known (assembly based on similarity)
  - [ ] genomic is incorporating tests to try to curate alignments better
  - [ ] but data from gene sequences can only be used in a gene alignment context, not genomic data
